---
title: "Market_Mix"
author: "Harsh Shukla,Priya Agrawal"
date: "17 July 2018"
output: html_document
runtime: shiny

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

```{r echo=FALSE, warning=FALSE, paged.print=FALSE}
options(warn=-1)
library(ggplot2);
library(plyr);
library(dplyr);
library(Hmisc);
library(broom);
library(xts);
library(lubridate)
library(cluster)
library(zoo)
library(magrittr)
options(warn=-1)


#gaming_accesory <- read.csv("gaming_accesory")
camera_accesory <- read.csv("CameraAccessory")
#home_audio      <- read.csv("home_audio")
#print(head(camera_accesory))
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# KPI Function
KPI_FN <- function(dataset){
    ##1.Adstock Data 
advertisement<-read.csv("advertisement.csv")
    adstock <- subset(advertisement, select=c(-Total.Investment))    
    #Dividing by 4.29 
    for( i in 3:ncol(adstock)){
        adstock[,i] = adstock[,i]/(4.29)
    }  
    merge(dataset, adstock, by=c("Year","Month"), all.x = TRUE)
    dataset[is.na(dataset)] <- 0
    ##2.Discount
    dataset$list_price = dataset$gmv/dataset$units
    #Discount = List Price - Discount
    dataset$promotional_offer = (dataset$product_mrp - dataset$list_price)/dataset$product_mrp
    ##3.Payment Model Indicator
    dataset$order_pay_id <- ifelse(dataset$s1_fact.order_payment_type   == "Prepaid",1,0)
    
    ##4.Prepaid Order %
    #Total Order Placed
    total_order <-aggregate(order_pay_id ~ Year+Month+week_year,data=dataset, FUN=NROW)
    #Total Online Order 
    online_order <- aggregate(order_pay_id~Year+Month+week_year, data= dataset, FUN=sum)
    #merge both the files
    merged <- merge(total_order,online_order,by=c("Month", "Year", "week_year"),all.x=TRUE)
    #calculating per online order  
    merged$per_order <- merged$order_pay_id.y / merged$order_pay_id.x
    #remove other variabled from 
    #merge with dataset file    
    merged <- merged[,-c(4,5)]
    #add per_order in dataset file
    dataset <- merge(dataset, merged, by=c("Month", "Year", "week_year"),all.x=TRUE)  
    dataset[is.na(dataset)] <- 0
    ##5.Brand Perception - Product Category
    dataset$product_analytic_vertical <- factor(dataset$product_analytic_vertical) 
    cluster <- aggregate(cbind(units,list_price,product_mrp)~product_analytic_vertical,dataset,mean)
    if(nrow(cluster) >2){
        cluster$list_price_1 <- scale(cluster$list_price)
        cluster$product_mrp_1 <- scale(cluster$product_mrp)
        cluster$units_1 <- scale(cluster$units)
        k1 <- cluster[,-c(2:4)]
      
        clust <- kmeans(k1[-1], centers=3,iter.max=50,nstart=50) 
        cluster$P_tag <- as.factor(clust$cluster)
        cluster <- cluster[,c(1,8)]        
    #   add extra column in dataset
        dataset <- merge(dataset,cluster,by=c("product_analytic_vertical"), all.x=TRUE)
        
        k2 <- table(dataset$P_tag)
    
        levels(dataset$P_tag)[which(k2==max(table(dataset$P_tag)))] <- "Mass_p"
        levels(dataset$P_tag)[which(k2==min(table(dataset$P_tag)))] <- "Premium_p"
        levels(dataset$P_tag)[which(k2!=max(table(dataset$P_tag))& k2!=min(table(dataset$P_tag)))] <- "Middle_p"
       }
    else 
    {
        dataset$P_tag <- NA
        dataset$product_analytic_vertical <- factor(dataset$product_analytic_vertical) 
        if(tapply(dataset$product_mrp, dataset$product_analytic_vertical,mean)[[1]] > (tapply(dataset$product_mrp,dataset$product_analytic_vertical,mean)[[2]]))
        {
            dataset$P_tag[which(dataset$product_analytic_vertical == levels(dataset$product_analytic_vertical)[1])] <- "middle"
            dataset$P_tag[is.na(dataset$P_tag)] <- "mass"
        }
        else
        {
            dataset$P_tag[which(dataset$product_analytic_vertical == levels(dataset$product_analytic_vertical)[2])] <- "middle"
            dataset$P_tag[is.na(dataset$P_tag)] <- "mass"
        }
    }
    count <- table(dataset$P_tag)
    barplot(count, main= "Brand Perception",xlab="Type of Product for Market")
     
    ##6. NPS_Score
        nps <-read.csv('nps.csv',h=T)
        nps$Month <- as.character(nps$Month)
        dataset <- merge(dataset,nps,by=c("Month","Year"),all.x=TRUE)
    
    ##7. Total Investment across all Channels
        inv <- advertisement
        inv$Month <- as.character(inv$Month)
        inv$Year  <- as.character(inv$Year)
        dataset <- merge(dataset,inv,by=c("Month","Year"),all.x=TRUE)
    
    ##8. Holiday Effect 
    
        holiday_list<-c("2015-07-18","2015-07-19","2015-08-15",
                  "2015-08-16","2015-08-17","2015-08-28",
                  "2015-08-29","2015-08-30","2015-10-15",
                  "2015-10-16","2015-10-17","2015-11-07","2015-11-08","2015-11-09","2015-11-10",
                  "2015-10-11","2015-10-12","2015-11-13","2015-11-14","2015-12-25","2015-12-26",
                  "2015-12-27","2015-12-28","2015-12-29","2015-12-30","2016-01-01","2016-01-02",
                  "2016-01-03","2016-01-20","2016-01-21","2016-01-22","2016-02-01","2016-02-02",
                  "2016-02-20","2016-02-21","2016-02-14","2016-02-15","2016-03-07","2016-03-08",
                  "2016-03-09","2016-05-25","2016-05-26","2016-05-27")
        
        holiday_list <- as.Date(holiday_list)
        week_year <- week(holiday_list)
        year <- year(holiday_list)
        holiday_data <- data.frame(cbind(year,week_year))
        holiday_data$holiday_list <- holiday_list
        holiday_data$number <- 1
        holiday_data <- aggregate(number~year+week_year,holiday_data, sum)
      #  write.csv(holiday_data,"holiday_data.csv",row.names=F)
        
        dataset$paste <-paste(dataset$Year, dataset$week_year, sep='_')
        products <- as.data.frame.matrix(t(table(dataset$P_tag,dataset$week_year)))
        products$week_year <- row.names(products)
    
        holiday_data$paste <-paste(holiday_data$year, holiday_data$week_year, sep='_')
        holiday_data <- holiday_data[,-c(1:2)]
        dataset <- merge(dataset, holiday_data, by=c("paste"),all.x=TRUE)
    
        dataset$number[is.na(dataset$number)] <- 0
        dataset <- aggregate(cbind(list_price,product_mrp,gmv,units,sla,promotional_offer,Total.Investment,TV,Digital,Sponsorship,Content.Marketing,Online.marketing,Affiliates,SEM,product_procurement_sla,per_order,NPS)~week_year,data=dataset,FUN=mean)   
        dataset <- merge(dataset,products,by=c("week_year"),all.x=TRUE)
        
        
    return(dataset)
}
```


```{r echo=FALSE}
#home_audio_FE <- KPI_FN(home_audio)
#gaming_accesory_FE <- KPI_FN(gaming_accesory)
camera_accesory_FE <- KPI_FN(camera_accesory)
print(summary(camera_accesory_FE))
```

```{r echo=FALSE}
advanced_kpi <- function(dataset){
  library(dplyr)
  library(zoo)
  
  myfun1 = function(x) rollmean(x, k = 2, fill = NA, align = "right")
  myfun2 = function(x) rollmean(x, k = 3, fill = NA, align = "right")
  myfun3 = function(x) rollmean(x, k = 4, fill = NA, align = "right")
  
  #dataset1<-arrange(dataset1,P_analytic_vertical,Year,week_year)
  
  x=dataset[,c("week_year","list_price","promotional_offer")]
  
  
  x1<-x %>% mutate_each(funs(myfun1),list_price,promotional_offer) %>% data.frame()
  
  x2<-x %>% mutate_each(funs(myfun2),list_price,promotional_offer) %>% data.frame()
  
  x3<-x %>% mutate_each(funs(myfun3),list_price,promotional_offer) %>% data.frame()
  
  
  x1$LP_MA1<-(x1$list_price)
  x1$PO_MA1<-(x1$promotional_offer)
  
  x2$LP_MA2<-(x2$list_price)
  x2$PO_MA2<-(x2$promotional_offer)
  
  x3$LP_MA3<-(x3$list_price)
  x3$PO_MA3<-(x3$promotional_offer)
  
  x4=cbind(x1[,-c(2:3)],x2[,-c(1:3)],x3[,-c(1:3)])
  
   dataset<-merge(dataset,x4,by="week_year")
    
  dataset$inc_LP_MA1<-(dataset$list_price - dataset$LP_MA1)/dataset$LP_MA1
  dataset$inc_LP_MA2<-(dataset$list_price - dataset$LP_MA2)/dataset$LP_MA2
  dataset$inc_LP_MA3<-(dataset$list_price - dataset$LP_MA3)/dataset$LP_MA3
  
  dataset$inc_PO_MA1<-(dataset$promotional_offer - dataset$PO_MA1)/dataset$PO_MA1
  dataset$inc_PO_MA2<-(dataset$promotional_offer - dataset$PO_MA2)/dataset$PO_MA2
  dataset$inc_PO_MA3<-(dataset$promotional_offer - dataset$PO_MA3)/dataset$PO_MA3
  
  #Deleting some columns

  
  dataset$LP_MA1<-NULL
  dataset$LP_MA2<-NULL
  dataset$LP_MA3<-NULL
  
  dataset$PO_MA1<-NULL
  dataset$PO_MA2<-NULL
  dataset$PO_MA3<-NULL
  
  names(dataset)[21:26]<-c("inc_LP_MA1","inc_LP_MA2","inc_LP_MA3","inc_PO_MA1","inc_PO_MA2",
                           "inc_PO_MA3")
    
  #------1) Lag of List price by 1 week,2 week, 3 week
  #------2) Lag of discount(promo_off) by 1 week,2 week, 3 week
  #------3) Incremental Lag of List price & promotions/discounts by 1 week,2 week, 3 week
  
  #-----------------Lag the data after aggregating by week----#
  
  #8. Lag List price (different period lags)
  library(DataCombine)
  
  data_dum <- slide(dataset,Var="list_price",slideBy=-1)
  data_dum <- slide(data_dum,Var="list_price",slideBy=-2)
  data_dum <- slide(data_dum,Var="list_price",slideBy=-3)
    
  data_dum <- slide(data_dum,Var="promotional_offer",slideBy=-1)
  data_dum <- slide(data_dum,Var="promotional_offer",slideBy=-2)
  data_dum <- slide(data_dum,Var="promotional_offer",slideBy=-3)

  data_dum <- slide(data_dum,Var="NPS",slideBy=-1)
  data_dum <- slide(data_dum,Var="NPS",slideBy=-2)
  data_dum <- slide(data_dum,Var="NPS",slideBy=-3)
    
  dataset <- na.omit(data_dum)
    
  return (dataset)
  
}


#home_audio_final <- advanced_kpi(home_audio_FE)
#gaming_accesory_final <- advanced_kpi(gaming_accesory_FE)
camera_accesory_final <- advanced_kpi(camera_accesory_FE)

summary(camera_accesory_final)

#summary(home_audio_final)

#summary(gaming_accesory_final)

eda <- function(dataset,name){
    #AdStock
    plot1 <- ggplot(dataset,aes(TV,gmv))+geom_point()+geom_smooth(aes=(method="lm"))+ggtitle(name)+labs(x="Adstock TV ",y="GMV")
    plot1
    
    plot2 <-ggplot(dataset,aes(Affiliates,gmv))+geom_point()+geom_smooth(aes=(method="lm"))+ggtitle(name)+labs(x="Affiliates ",y="GMV")
    plot2
    
    plot3 <-ggplot(dataset,aes(Content.Marketing,gmv))+geom_point()+geom_smooth(aes=(method="lm"))+ggtitle(name)+labs(x="Content Marketing",y="GMV")
    plot3
    
    plot4 <-ggplot(dataset,aes(Online.marketing,gmv))+geom_point()+geom_smooth(aes=(method="lm"))+ggtitle(name)+labs(x="Online Marketing",y="GMV")
    plot4
    
    plot5 <-ggplot(dataset,aes(SEM,gmv))+geom_point()+geom_smooth(aes=(method="lm"))+ggtitle(name)+labs(x="SEM Adstock ",y="GMV")
    plot5
    
    plot6 <-ggplot(dataset,aes(Digital,gmv))+geom_point()+geom_smooth(aes=(method="lm"))+ggtitle(name)+labs(x="Digital Adstock ",y="GMV")
    plot6
    
    return(list(plot1,plot2,plot3,plot4,plot5,plot6))
    
    
}
#plots_home_audio <- eda(home_audio_final,'home_audio')
#plots_home_audio

#plots_gaming_accesory <- eda(gaming_accesory_final,'home_audio')
#plots_gaming_accesory

plots_camera_accesory <- eda(camera_accesory_final,'camera_accesory')
plots_camera_accesory
```


'''## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```


