---
title: "Market_Mix"
author: "Harsh Shukla,Priya Agrawal"
date: "17 July 2018"
runtime: shiny
---








This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
options(warn=-1)
library(ggplot2);
library(plyr);
library(dplyr);
library(Hmisc);
library(broom);
library(xts);
library(lubridate)
library(cluster)
library(zoo)
library(magrittr)
options(warn=-1)


#gaming_accesory <- read.csv("gaming_accesory")
data = read.csv("CameraAccessory")
#home_audio      <- read.csv("home_audio")
#print(head(camera_accesory))

KPI_FN <- function(dataset){
    ##1.Adstock Data 
    advertisement <- read.csv("advertisement.csv")
    adstock <- subset(advertisement, select=c(-Total.Investment))    
    #Dividing by 4.29 
    for( i in 3:ncol(adstock)){
        adstock[,i] = adstock[,i]/(4.29)
    }  
    merge(dataset, adstock, by=c("Year","Month"), all.x = TRUE)
    dataset[is.na(dataset)] <- 0
    ##2.Discount
    dataset$list_price = dataset$gmv/dataset$units
    #Discount = List Price - Discount
    dataset$promotional_offer = (dataset$product_mrp - dataset$list_price)/dataset$product_mrp
    ##3.Payment Model Indicator
    dataset$order_pay_id <- ifelse(dataset$s1_fact.order_payment_type   == "Prepaid",1,0)
    
    ##4.Prepaid Order %
    #Total Order Placed
    total_order <-aggregate(order_pay_id ~ Year+Month+week_year,data=dataset, FUN=NROW)
    #Total Online Order 
    online_order <- aggregate(order_pay_id~Year+Month+week_year, data= dataset, FUN=sum)
    #merge both the files
    merged <- merge(total_order,online_order,by=c("Month", "Year", "week_year"),all.x=TRUE)
    #calculating per online order  
    merged$per_order <- merged$order_pay_id.y / merged$order_pay_id.x
    #remove other variabled from 
    #merge with dataset file    
    merged <- merged[,-c(4,5)]
    #add per_order in dataset file
    dataset <- merge(dataset, merged, by=c("Month", "Year", "week_year"),all.x=TRUE)  
    dataset[is.na(dataset)] <- 0
    ##5.Brand Perception - Product Category
    dataset$product_analytic_vertical <- factor(dataset$product_analytic_vertical) 
    cluster <- aggregate(cbind(units,list_price,product_mrp)~product_analytic_vertical,dataset,mean)
    if(nrow(cluster) >2){
        cluster$list_price_1 <- scale(cluster$list_price)
        cluster$product_mrp_1 <- scale(cluster$product_mrp)
        cluster$units_1 <- scale(cluster$units)
        k1 <- cluster[,-c(2:4)]
      
        clust <- kmeans(k1[-1], centers=3,iter.max=50,nstart=50) 
        cluster$P_tag <- as.factor(clust$cluster)
        cluster <- cluster[,c(1,8)]        
    #   add extra column in dataset
        dataset <- merge(dataset,cluster,by=c("product_analytic_vertical"), all.x=TRUE)
        library("plyr")
        library("dplyr")
    
        k2 <- table(dataset$P_tag)
    
        levels(dataset$P_tag)[which(k2==max(table(dataset$P_tag)))] <- "Mass_p"
        levels(dataset$P_tag)[which(k2==min(table(dataset$P_tag)))] <- "Premium_p"
        levels(dataset$P_tag)[which(k2!=max(table(dataset$P_tag))& k2!=min(table(dataset$P_tag)))] <- "Middle_p"
       }
    else 
    {
        dataset$P_tag <- NA
        dataset$product_analytic_vertical <- factor(dataset$product_analytic_vertical) 
        if(tapply(dataset$product_mrp, dataset$product_analytic_vertical,mean)[[1]] > (tapply(dataset$product_mrp,dataset$product_analytic_vertical,mean)[[2]]))
        {
            dataset$P_tag[which(dataset$product_analytic_vertical == levels(dataset$product_analytic_vertical)[1])] <- "middle"
            dataset$P_tag[is.na(dataset$P_tag)] <- "mass"
        }
        else
        {
            dataset$P_tag[which(dataset$product_analytic_vertical == levels(dataset$product_analytic_vertical)[2])] <- "middle"
            dataset$P_tag[is.na(dataset$P_tag)] <- "mass"
        }
    }
    count <- table(dataset$P_tag)
    barplot(count, main= "Brand Perception",xlab="Type of Product for Market")
     
    ##6. NPS_Score
        nps <-read.csv('nps.csv',h=T)
        nps$Month <- as.character(nps$Month)
        dataset <- merge(dataset,nps,by=c("Month","Year"),all.x=TRUE)
    
    ##7. Total Investment across all Channels
        inv <- advertisement
        inv$Month <- as.character(inv$Month)
        inv$Year  <- as.character(inv$Year)
        dataset <- merge(dataset,inv,by=c("Month","Year"),all.x=TRUE)
    
    ##8. Holiday Effect 
    
        holiday_list<-c("2015-07-18","2015-07-19","2015-08-15",
                  "2015-08-16","2015-08-17","2015-08-28",
                  "2015-08-29","2015-08-30","2015-10-15",
                  "2015-10-16","2015-10-17","2015-11-07","2015-11-08","2015-11-09","2015-11-10",
                  "2015-10-11","2015-10-12","2015-11-13","2015-11-14","2015-12-25","2015-12-26",
                  "2015-12-27","2015-12-28","2015-12-29","2015-12-30","2016-01-01","2016-01-02",
                  "2016-01-03","2016-01-20","2016-01-21","2016-01-22","2016-02-01","2016-02-02",
                  "2016-02-20","2016-02-21","2016-02-14","2016-02-15","2016-03-07","2016-03-08",
                  "2016-03-09","2016-05-25","2016-05-26","2016-05-27")
        
        holiday_list <- as.Date(holiday_list)
        week_year <- week(holiday_list)
        year <- year(holiday_list)
        holiday_data <- data.frame(cbind(year,week_year))
        holiday_data$holiday_list <- holiday_list
        holiday_data$number <- 1
        holiday_data <- aggregate(number~year+week_year,holiday_data, sum)
        write.csv(holiday_data,"holiday_data.csv",row.names=F)
        
        dataset$paste <-paste(dataset$Year, dataset$week_year, sep='_')
        products <- as.data.frame.matrix(t(table(dataset$P_tag,dataset$week_year)))
        products$week_year <- row.names(products)
    
        holiday_data$paste <-paste(holiday_data$year, holiday_data$week_year, sep='_')
        holiday_data <- holiday_data[,-c(1:2)]
        dataset <- merge(dataset, holiday_data, by=c("paste"),all.x=TRUE)
    
        dataset$number[is.na(dataset$number)] <- 0
        dataset <- aggregate(cbind(list_price,product_mrp,gmv,units,sla,promotional_offer,number,Total.Investment,TV,Digital,Sponsorship,Content.Marketing,Online.marketing,Affiliates,SEM,product_procurement_sla,per_order,NPS)~week_year,data=dataset,FUN=mean)   
        dataset <- merge(dataset,products,by=c("week_year"),all.x=TRUE)
        
    return(dataset)
}

#home_audio_FE <- KPI_FN(home_audio)
#gaming_accesory_FE <- KPI_FN(gaming_accesory)
data_FE <- KPI_FN(data)



advanced_kpi <- function(dataset){
  library(dplyr)
  library(zoo)
  
  myfun1 = function(x) rollmean(x, k = 2, fill = NA, align = "right")
  myfun2 = function(x) rollmean(x, k = 3, fill = NA, align = "right")
  myfun3 = function(x) rollmean(x, k = 4, fill = NA, align = "right")
  
  #dataset1<-arrange(dataset1,P_analytic_vertical,Year,week_year)
  
  x=dataset[,c("week_year","list_price","promotional_offer")]
  
  
  x1<-x %>% mutate_each(funs(myfun1),list_price,promotional_offer) %>% data.frame()
  
  x2<-x %>% mutate_each(funs(myfun2),list_price,promotional_offer) %>% data.frame()
  
  x3<-x %>% mutate_each(funs(myfun3),list_price,promotional_offer) %>% data.frame()
  
  
  x1$LP_MA1<-(x1$list_price)
  x1$PO_MA1<-(x1$promotional_offer)
  
  x2$LP_MA2<-(x2$list_price)
  x2$PO_MA2<-(x2$promotional_offer)
  
  x3$LP_MA3<-(x3$list_price)
  x3$PO_MA3<-(x3$promotional_offer)
  
  x4=cbind(x1[,-c(2:3)],x2[,-c(1:3)],x3[,-c(1:3)])
  
   dataset<-merge(dataset,x4,by="week_year")
    
  dataset$inc_LP_MA1<-(dataset$list_price - dataset$LP_MA1)/dataset$LP_MA1
  dataset$inc_LP_MA2<-(dataset$list_price - dataset$LP_MA2)/dataset$LP_MA2
  dataset$inc_LP_MA3<-(dataset$list_price - dataset$LP_MA3)/dataset$LP_MA3
  
  dataset$inc_PO_MA1<-(dataset$promotional_offer - dataset$PO_MA1)/dataset$PO_MA1
  dataset$inc_PO_MA2<-(dataset$promotional_offer - dataset$PO_MA2)/dataset$PO_MA2
  dataset$inc_PO_MA3<-(dataset$promotional_offer - dataset$PO_MA3)/dataset$PO_MA3
  
  #Deleting some columns
  dataset$LP_MA1<-NULL
  dataset$LP_MA2<-NULL
  dataset$LP_MA3<-NULL
  
  dataset$PO_MA1<-NULL
  dataset$PO_MA2<-NULL
  dataset$PO_MA3<-NULL
  
  names(dataset)[23:28]<-c("inc_LP_MA1","inc_LP_MA2","inc_LP_MA3","inc_PO_MA1","inc_PO_MA2",
                           "inc_PO_MA3")
    
  #------1) Lag of List price by 1 week,2 week, 3 week
  #------2) Lag of discount(promo_off) by 1 week,2 week, 3 week
  #------3) Incremental Lag of List price & promotions/discounts by 1 week,2 week, 3 week
  
  #-----------------Lag the data after aggregating by week----#
  
  #8. Lag List price (different period lags)
  library(DataCombine)
  
  data_dum <- slide(dataset,Var="list_price",slideBy=-1)
  data_dum <- slide(data_dum,Var="list_price",slideBy=-2)
  data_dum <- slide(data_dum,Var="list_price",slideBy=-3)
  data_dum <- slide(data_dum,Var="promotional_offer",slideBy=-1)
  data_dum <- slide(data_dum,Var="promotional_offer",slideBy=-2)
  data_dum <- slide(data_dum,Var="promotional_offer",slideBy=-3)

  data_dum <- slide(data_dum,Var="NPS",slideBy=-1)
  data_dum <- slide(data_dum,Var="NPS",slideBy=-2)
  data_dum <- slide(data_dum,Var="NPS",slideBy=-3)
  dataset <- na.omit(data_dum)
  return (dataset)
}

#home_audio_final <- advanced_kpi(home_audio_FE)
#gaming_accesory_final <- advanced_kpi(gaming_accesory_FE)
data_final <- advanced_kpi(data_FE)
#summary(hme_audio_final)
#summary(gaming_accesory_final)



eda <- function(dataset,name){
    #AdStock
    plot1 <- ggplot(dataset,aes(TV,gmv))+geom_point()+geom_smooth(aes=(method="lm"))+ggtitle(name)+labs(x="Adstock TV ",y="GMV")
    plot1
    
    plot2 <-ggplot(dataset,aes(Affiliates,gmv))+geom_point()+geom_smooth(aes=(method="lm"))+ggtitle(name)+labs(x="Affiliates ",y="GMV")
    plot2
    
    plot3 <-ggplot(dataset,aes(Content.Marketing,gmv))+geom_point()+geom_smooth(aes=(method="lm"))+ggtitle(name)+labs(x="Content Marketing",y="GMV")
    plot3
    
    plot4 <-ggplot(dataset,aes(Online.marketing,gmv))+geom_point()+geom_smooth(aes=(method="lm"))+ggtitle(name)+labs(x="Online Marketing",y="GMV")
    plot4
    
    plot5 <-ggplot(dataset,aes(SEM,gmv))+geom_point()+geom_smooth(aes=(method="lm"))+ggtitle(name)+labs(x="SEM Adstock ",y="GMV")
    plot5
    
    plot6 <-ggplot(dataset,aes(Digital,gmv))+geom_point()+geom_smooth(aes=(method="lm"))+ggtitle(name)+labs(x="Digital Adstock ",y="GMV")
    plot6
    
    return(list(plot1,plot2,plot3,plot4,plot5,plot6))
}



#plots_home_audio <- eda(home_audio_final,'home_audio')
#plots_home_audio
#plots_gaming_accesory <- eda(gaming_accesory_final,'home_audio')
#plots_gaming_accesory
plots_data <- eda(data_final,'EDA')
print(plots_data)


# Building the Baisc Linear regression Model
Linear_model <-data_final
Linear_model <- scale(Linear_model)
Linear_model <-data.frame(Linear_model)
model_1 <- lm(gmv~.,Linear_model)
print(summary(model_1))

library(car)
library(MASS)

all_vifs <- vif(model_1)

 signif_all <- names(all_vifs)

 while(any(all_vifs > 2)){
  var_with_max_vif <- names(which(all_vifs == max(all_vifs)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=Linear_model)  # re-build model with new formula
  all_vifs <- vif(selectedMod)
}

##Final Model 
Linear_Final_model <- selectedMod
print(summary(Linear_Final_model))  



library(caret)
# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val <- train(myForm, data = Linear_model, method = "lm",
               trControl = train.control)
# Summarize the results
print(cross_val)


# Elasticity Analysis
train <- Linear_model
hrlm<-Linear_Final_model
# estimating the elasticity coefficients
elasticity <- function(var){
  
  elax1 <-as.numeric(hrlm$coefficients[var]*mean(train[,var])/mean(train$gmv))
  
  return(elax1)
} 
var_list <- list()

for(i in 2:length(hrlm$coefficients)){
  
  var_list[i-1] <-elasticity(names(hrlm$coefficients)[i])
  
}

elasticity.outputs <- data.frame(names(hrlm$coefficients[2:length(hrlm$coefficients)]))
elasticity.outputs <- cbind(elasticity.outputs,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs) <- c("Variable","Elasticity")

elasticity.outputs$direction <- ifelse(elasticity.outputs$Elasticity > 0, "Positive", "Negative")
print(elasticity.outputs)


print(ggplot(data=elasticity.outputs, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Camera Accesory - Linear Model") +xlab("Variables"))


multi <-data_final
multi <- multi[,-c(20:28)]
multi$number[which(multi$number==0)] <- 0.01
multi$Content.Marketing[which(multi$Content.Marketing==0)] <- 0.01
multi$per_order[which(multi$per_order==0)] <- 0.01
multi$TV[which(multi$TV==0)] <- 0.01
multi <- log(multi)
## First model ##
multi_model <- lm(gmv~.,multi)
print(summary(multi_model))

library(car)
library(MASS)

all_vifs <- vif(multi_model)

 signif_all <- names(all_vifs)

 while(any(all_vifs > 1.2)){
  var_with_max_vif <- names(which(all_vifs == max(all_vifs)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=multi)  # re-build model with new formula
  all_vifs <- vif(selectedMod)
}

Multi_Final_model <- selectedMod
print(summary(Multi_Final_model))


library(caret)
# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val1 <- train(myForm, data = multi, method = "lm",
               trControl = train.control)
# Summarize t1he results
print(cross_val1)

# Elasticity Analysis
train1 <- multi
hrlm1<-Multi_Final_model
# estimating the elasticity coefficients
elasticity1 <- function(var){
  
  elax2 <-as.numeric(hrlm1$coefficients[var]*mean(train1[,var])/mean(train1$gmv))
  
  return(elax2)
} 
var_list <- list()

for(i in 2:length(hrlm1$coefficients)){
  
  var_list[i-1] <-elasticity1(names(hrlm1$coefficients)[i])
  
}

elasticity.outputs1 <- data.frame(names(hrlm1$coefficients[2:length(hrlm1$coefficients)]))
elasticity.outputs1 <- cbind(elasticity.outputs1,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs1) <- c("Variable","Elasticity")

elasticity.outputs1$direction <- ifelse(elasticity.outputs1$Elasticity > 0, "Positive", "Negative")
print(elasticity.outputs1)


ggplot(data=elasticity.outputs1, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Camera Accesory- Multiplicative Model") +xlab("Variables")


library(DataCombine)
Home_koyck<-data_final
#gmv Lag 1
Home_Koyck<-slide(Home_koyck,Var="gmv",slideBy =-1)
Home_Koyck<-na.omit(Home_koyck)
Home_Koyck<-scale(Home_koyck)
Home_Koyck<-data.frame(Home_koyck)

# Build Kyock model
Koy_model <- lm(gmv~.,Home_koyck)
print(summary(Koy_model))



all_vifs <- vif(Koy_model)
 signif_all <- names(all_vifs)

 while(any(all_vifs > 2)){
  var_with_max_vif <- names(which(all_vifs == max(all_vifs)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=Home_koyck)  # re-build model with new formula
  all_vifs <- vif(selectedMod)
}

kyock_Final_model <- selectedMod
summary(kyock_Final_model)

library(caret)
# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val2 <- train(myForm, data = Home_koyck, method = "lm",
               trControl = train.control)
# Summarize t1he results
print(cross_val2)

# Elasticity Analysis
train2 <- Home_koyck
hrlm2<-kyock_Final_model
# estimating the elasticity coefficients
elasticity2 <- function(var){
  
  elax2 <-as.numeric(hrlm2$coefficients[var]*mean(train2[,var])/mean(train2$gmv))

  return(elax2)
} 
var_list <- list()

for(i in 2:length(hrlm2$coefficients)){
  
  var_list[i-1] <-elasticity2(names(hrlm2$coefficients)[i])
  
}

elasticity.outputs <- data.frame(names(hrlm2$coefficients[2:length(hrlm2$coefficients)]))
elasticity.outputs <- cbind(elasticity.outputs,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs) <- c("Variable","Elasticity")

elasticity.outputs$direction <- ifelse(elasticity.outputs$Elasticity > 0, "Positive", "Negative")



ggplot(data=elasticity.outputs, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Camera Accesory - Koyck Model") +xlab("Variables")

Dis_Model <- data_final
Dis_model <- slide(Dis_Model, Var = "gmv",slideBy = -1)
Dis_model <- slide(Dis_model, Var = "gmv",slideBy = -2)
Dis_model <- slide(Dis_model, Var = "gmv",slideBy = -3)
Dis_model <- na.omit(Dis_model)
Dis_model <- scale(Dis_model)
Dis_model <- data.frame(Dis_model)

dist_model <- lm(gmv~.,Dis_model)
print(summary(dist_model))


all_vif <- vif(dist_model)
signif_all <- names(all_vif)

 while(any(all_vif > 2)){
  var_with_max_vif <- names(which(all_vif == max(all_vif)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=Dis_model)  # re-build model with new formula
  all_vif <- vif(selectedMod)
}

Distributed_Final_model <- selectedMod
print(summary(Distributed_Final_model))


library(caret)
# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val <- train(myForm, data =Dis_model , method = "lm",
               trControl = train.control)
# Summarize t1he results
print(cross_val)

# Elasticity Analysis
train <- Dis_model
hrlm<-Distributed_Final_model
# estimating the elasticity coefficients
elasticity <- function(var){
  elax1 <-as.numeric(hrlm$coefficients[var]*mean(train[,var])/mean(train$gmv))
  return(elax1)
} 
var_list <- list()

for(i in 2:length(hrlm$coefficients)){
  
  var_list[i-1] <- elasticity(names(hrlm2$coefficients)[i])
  
}

elasticity.outputs <- data.frame(names(hrlm$coefficients[2:length(hrlm$coefficients)]))
elasticity.outputs <- cbind(elasticity.outputs,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs) <- c("Variable","Elasticity")

elasticity.outputs$direction <- ifelse(elasticity.outputs$Elasticity > 0, "Positive", "Negative")



ggplot(data=elasticity.outputs, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Camera Accesory- Distributed_lag Model") +xlab("Variables")

Multi_dist <-data_final[,-c(20:28)]
Multi_Dis_model_1 <- slide(Multi_dist, Var = "gmv",slideBy = -1)
Multi_Dis_model_1 <- slide(Multi_Dis_model_1, Var = "gmv",slideBy = -2)
Multi_Dis_model_1 <- slide(Multi_Dis_model_1, Var = "gmv",slideBy = -3)
Multi_dist <- na.omit(Multi_Dis_model_1)

Multi_dist$Content.Marketing[which(Multi_dist$Content.Marketing==0)] <-1
Multi_dist$per_order[which(Multi_dist$per_order==0)] <-0.01
Multi_dist$number[which(Multi_dist$number==0)] <-0.01
Multi_dist$TV[which(Multi_dist$TV==0)] <-0.01
Multi_dist <- log(Multi_dist)

distMulti <- lm(gmv~., Multi_dist)
print(summary(distMulti))


all_vif <- vif(distMulti )
signif_all <- names(all_vif)

 while(any(all_vif > 1.2)){
  var_with_max_vif <- names(which(all_vif == max(all_vif)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=Multi_dist)  # re-build model with new formula
  all_vif <- vif(selectedMod)
}

DistributedMulti_Final_model <- selectedMod
summary(DistributedMulti_Final_model)

library(caret)
# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val <- train(myForm, data =Multi_dist , method = "lm",
               trControl = train.control)
# Summarize t1he results
print(cross_val)

# estimating the elasticity coefficients
train <- Multi_dist

grlm <-DistributedMulti_Final_model 
elasticity <- function(var){
  
  elax1 <-as.numeric(grlm$coefficients[var]*mean(train[,var])/mean(train$gmv))
  
  return(elax1)
} 

var_list <- list()

for(i in 2:length(grlm$coefficients)){
  
  var_list[i-1] <-elasticity(names(grlm$coefficients)[i])
  
}

elasticity.outputs <- data.frame(names(grlm$coefficients[2:length(grlm$coefficients)]))
elasticity.outputs <- cbind(elasticity.outputs,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs) <- c("Variable","Elasticity")

elasticity.outputs$direction <- ifelse(elasticity.outputs$Elasticity > 0, "Positive", "Negative")



ggplot(data=elasticity.outputs, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Game Accessory - Multi. & DL model") +xlab("Variables")

```
## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)


```


