---
title: "Model Building"
author: " Priya Agrawal, Harsh Shukla"
date: "17 July 2018"
runtime: shiny
output: 
      flexdashboard::flex_dashboard:
        orientation: column
        vertical_layout: scroll
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Model Description {data-navmenu="Project Sections"}
### Basic Steps in the Model

* Apply the Particular Model

* Apply Variation Inflation Factor(vif) on that Model

* Cross validation of that Model

* Calculation of Elasticity

* Plot the result

### Simple Linear Model
The aim of linear regression is to model a continuous variable Y as a mathematical function of one or more X variable(s), so that we can use this regression model to predict the Y when only the X is known. This mathematical equation can be generalized as follows:
 
  Y = β1 + β2X + ϵ

where, β1 is the intercept and β2 is the slope. Collectively, they are called regression coefficients. ϵ is the error term, the part of Y the regression model is unable to explain.

### Multiplicative Model
This model assumes that as the data increase, so does the seasonal pattern. Most time series plots exhibit such a pattern. In this model, the trend and seasonal components are multiplied and then added to the error component.
Multiplicative model’s benefits include synergistic impact of **marketing activities, independence of shapes of transformations** independent variable scan take due to coefficient values and coefficients directly provide simple elasticity indications.

### Kyock Model
The Koyck model may be considered a simple augmentation of the basic linear model , which includes the lagged dependent variable as independent variable.What this specification means is that sales depend on sales of the prior period and all the independent variables that caused prior sales,plus the current values of the same independent variables

### Distributed Lag Model
A distributed-lag model is a dynamic model in which the effect of a regressor x on y occurs over time rather than all at once.
The distributed lag model is a model with multiple lagged values of both the dependent variable and the independent variable.
This model is very general and can capture a whole range of carryover effects. Indeed, the Koyck model can be considered a special case
of distributed lag model with only one lagged value of the dependent variable. The distributed lag model overcomes two of the problems with the Koyck model.
First, ***it allows for decay functions, which are nonmonotonic or humped shaped***. 
Second, ***it can partly separate out the carryover effects of different independent variables***.

### Multiplicative +Distributed Lag Model




# Model on Home Audio Accessories Final {data-navmenu="Project Sections"}



```{r echo=FALSE}
options(warn=-1)
library(magrittr)
library(knitr)
library(DT)
library(ggplot2);
library(plyr);
library(dplyr);
library(Hmisc);
library(broom);
library(xts);
library(lubridate)
library(cluster)
library(zoo)
library(car)
library(MASS)
library(caret)
library(DataCombine)
options(warn=-1)
# Function for Various Model
data_final <- read.csv("home_audio_final")
# Building the Baisc Linear regression Model
Linear_model <-data_final
Linear_model <- scale(Linear_model)
Linear_model <-data.frame(Linear_model)
model_1 <- lm(gmv~.,Linear_model)



all_vifs <- vif(model_1)

 signif_all <- names(all_vifs)

 while(any(all_vifs > 2)){
  var_with_max_vif <- names(which(all_vifs == max(all_vifs)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=Linear_model)  # re-build model with new formula
  all_vifs <- vif(selectedMod)
}

##Final Model 
Linear_Final_model <- selectedMod





# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val <- train(myForm, data = Linear_model, method = "lm",
               trControl = train.control)




# Elasticity Analysis
train <- Linear_model
hrlm<-Linear_Final_model
# estimating the elasticity coefficients
elasticity <- function(var){
  
  elax1 <-as.numeric(hrlm$coefficients[var]*mean(train[,var])/mean(train$gmv))
  
  return(elax1)
} 
var_list <- list()

for(i in 2:length(hrlm$coefficients)){
  
  var_list[i-1] <-elasticity(names(hrlm$coefficients)[i])
  
}

elasticity.outputs <- data.frame(names(hrlm$coefficients[2:length(hrlm$coefficients)]))
elasticity.outputs <- cbind(elasticity.outputs,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs) <- c("Variable","Elasticity")

elasticity.outputs$direction <- ifelse(elasticity.outputs$Elasticity > 0, "Positive", "Negative")



print(ggplot(data=elasticity.outputs, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Home_Audio - Linear Model") +xlab("Variables"))


multi <-data_final
multi <- multi[,-c(20:28)]
multi$number[which(multi$number==0)] <- 0.01
multi$Content.Marketing[which(multi$Content.Marketing==0)] <- 0.01
multi$per_order[which(multi$per_order==0)] <- 0.01
multi$TV[which(multi$TV==0)] <- 0.01
multi <- log(multi)
## First model ##
multi_model <- lm(gmv~.,multi)



all_vifs <- vif(multi_model)

 signif_all <- names(all_vifs)

 while(any(all_vifs > 1.1)){
  var_with_max_vif <- names(which(all_vifs == max(all_vifs)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=multi)  # re-build model with new formula
  all_vifs <- vif(selectedMod)
}

Multi_Final_model <- selectedMod




# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val1 <- train(myForm, data = multi, method = "lm",
               trControl = train.control)


# Elasticity Analysis
train1 <- multi
hrlm1<-Multi_Final_model
# estimating the elasticity coefficients
elasticity1 <- function(var){
  
  elax2 <-as.numeric(hrlm1$coefficients[var]*mean(train1[,var])/mean(train1$gmv))
  
  return(elax2)
} 
var_list <- list()

for(i in 2:length(hrlm1$coefficients)){
  
  var_list[i-1] <-elasticity1(names(hrlm1$coefficients)[i])
  
}

elasticity.outputs1 <- data.frame(names(hrlm1$coefficients[2:length(hrlm1$coefficients)]))
elasticity.outputs1 <- cbind(elasticity.outputs1,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs1) <- c("Variable","Elasticity")

elasticity.outputs1$direction <- ifelse(elasticity.outputs1$Elasticity > 0, "Positive", "Negative")



ggplot(data=elasticity.outputs1, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Home_Audio- Multiplicative Model") +xlab("Variables")



Home_koyck<-data_final
#gmv Lag 1
Home_Koyck<-slide(Home_koyck,Var="gmv",slideBy =-1)
Home_Koyck<-na.omit(Home_koyck)
Home_Koyck<-scale(Home_koyck)
Home_Koyck<-data.frame(Home_koyck)

# Build Kyock model
Koy_model <- lm(gmv~.,Home_koyck)
all_vifs <- vif(Koy_model)
 signif_all <- names(all_vifs)

 while(any(all_vifs > 2)){
  var_with_max_vif <- names(which(all_vifs == max(all_vifs)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=Home_koyck)  # re-build model with new formula
  all_vifs <- vif(selectedMod)
}

kyock_Final_model <- selectedMod



# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val2 <- train(myForm, data = Home_koyck, method = "lm",
               trControl = train.control)
# Summarize t1he results


# Elasticity Analysis
train2 <- Home_koyck
hrlm2<-kyock_Final_model
# estimating the elasticity coefficients
elasticity2 <- function(var){
  
  elax2 <-as.numeric(hrlm2$coefficients[var]*mean(train2[,var])/mean(train2$gmv))

  return(elax2)
} 
var_list <- list()

for(i in 2:length(hrlm2$coefficients)){
  
  var_list[i-1] <-elasticity2(names(hrlm2$coefficients)[i])
  
}

elasticity.outputs <- data.frame(names(hrlm2$coefficients[2:length(hrlm2$coefficients)]))
elasticity.outputs <- cbind(elasticity.outputs,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs) <- c("Variable","Elasticity")

elasticity.outputs$direction <- ifelse(elasticity.outputs$Elasticity > 0, "Positive", "Negative")



ggplot(data=elasticity.outputs, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Home_Audio - Koyck Model") +xlab("Variables")

Dis_Model <- data_final
Dis_model <- slide(Dis_Model, Var = "gmv",slideBy = -1)
Dis_model <- slide(Dis_model, Var = "gmv",slideBy = -2)
Dis_model <- slide(Dis_model, Var = "gmv",slideBy = -3)
Dis_model <- na.omit(Dis_model)
Dis_model <- scale(Dis_model)
Dis_model <- data.frame(Dis_model)

dist_model <- lm(gmv~.,Dis_model)



all_vif <- vif(dist_model)
signif_all <- names(all_vif)

 while(any(all_vif > 2)){
  var_with_max_vif <- names(which(all_vif == max(all_vif)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=Dis_model)  # re-build model with new formula
  all_vif <- vif(selectedMod)
}

Distributed_Final_model <- selectedMod




# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val <- train(myForm, data =Dis_model , method = "lm",
               trControl = train.control)
# Summarize t1he results


# Elasticity Analysis
train <- Dis_model
hrlm<-Distributed_Final_model
# estimating the elasticity coefficients
elasticity <- function(var){
  elax1 <-as.numeric(hrlm$coefficients[var]*mean(train[,var])/mean(train$gmv))
  return(elax1)
} 
var_list <- list()

for(i in 2:length(hrlm$coefficients)){
  
  var_list[i-1] <- elasticity(names(hrlm$coefficients)[i])
  
}

elasticity.outputs <- data.frame(names(hrlm$coefficients[2:length(hrlm$coefficients)]))
elasticity.outputs <- cbind(elasticity.outputs,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs) <- c("Variable","Elasticity")

elasticity.outputs$direction <- ifelse(elasticity.outputs$Elasticity > 0, "Positive", "Negative")



ggplot(data=elasticity.outputs, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Home_Audio- Distributed_lag Model") +xlab("Variables")


Multi_dist <-data_final[,-c(20:28)]
Multi_Dis_model_1 <- slide(Multi_dist, Var = "gmv",slideBy = -1)
Multi_Dis_model_1 <- slide(Multi_Dis_model_1, Var = "gmv",slideBy = -2)
Multi_Dis_model_1 <- slide(Multi_Dis_model_1, Var = "gmv",slideBy = -3)
Multi_dist <- na.omit(Multi_Dis_model_1)

Multi_dist$Content.Marketing[which(Multi_dist$Content.Marketing==0)] <-1
Multi_dist$per_order[which(Multi_dist$per_order==0)] <-0.01
Multi_dist$number[which(Multi_dist$number==0)] <-0.01
Multi_dist$TV[which(Multi_dist$TV==0)] <-0.01
Multi_dist <- log(Multi_dist)

distMulti <- lm(gmv~., Multi_dist)



all_vif <- vif(distMulti )
signif_all <- names(all_vif)

 while(any(all_vif > 1.2)){
  var_with_max_vif <- names(which(all_vif == max(all_vif)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=Multi_dist)  # re-build model with new formula
  all_vif <- vif(selectedMod)
}

DistributedMulti_Final_model <- selectedMod



# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val <- train(myForm, data =Multi_dist , method = "lm",
               trControl = train.control)
# Summarize t1he results


# estimating the elasticity coefficients
train <- Multi_dist

grlm <-DistributedMulti_Final_model 
elasticity <- function(var){
  
  elax1 <-as.numeric(grlm$coefficients[var]*mean(train[,var])/mean(train$gmv))
  
  return(elax1)
} 

var_list <- list()

for(i in 2:length(grlm$coefficients)){
  
  var_list[i-1] <-elasticity(names(grlm$coefficients)[i])
  
}

elasticity.outputs <- data.frame(names(grlm$coefficients[2:length(grlm$coefficients)]))
elasticity.outputs <- cbind(elasticity.outputs,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs) <- c("Variable","Elasticity")

elasticity.outputs$direction <- ifelse(elasticity.outputs$Elasticity > 0, "Positive", "Negative")



ggplot(data=elasticity.outputs, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Home_Audio - Multi. & DL model") +xlab("Variables")



```

# Model on camera  Accessories Final {data-navmenu="Project Sections"}
```{r echo=FALSE}

options(warn=-1)
library(magrittr)
library(knitr)
library(DT)
library(ggplot2);
library(plyr);
library(dplyr);
library(Hmisc);
library(broom);
library(xts);
library(lubridate)
library(cluster)
library(zoo)
library(car)
library(MASS)
library(caret)
library(DataCombine)
options(warn=-1)
# Function for Various Model
data1_final <- read.csv("camera_accesory_final")
# Building the Baisc Linear regression Model
Linear_model <-data1_final
Linear_model <- scale(Linear_model)
Linear_model <-data.frame(Linear_model)
model_1 <- lm(gmv~.,Linear_model)



all_vifs <- vif(model_1)

 signif_all <- names(all_vifs)

 while(any(all_vifs > 2)){
  var_with_max_vif <- names(which(all_vifs == max(all_vifs)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=Linear_model)  # re-build model with new formula
  all_vifs <- vif(selectedMod)
}

##Final Model 
Linear_Final_model <- selectedMod





# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val <- train(myForm, data = Linear_model, method = "lm",
               trControl = train.control)
# Summarize the results



# Elasticity Analysis
train <- Linear_model
hrlm<-Linear_Final_model
# estimating the elasticity coefficients
elasticity <- function(var){
  
  elax1 <-as.numeric(hrlm$coefficients[var]*mean(train[,var])/mean(train$gmv))
  
  return(elax1)
} 
var_list <- list()

for(i in 2:length(hrlm$coefficients)){
  
  var_list[i-1] <-elasticity(names(hrlm$coefficients)[i])
  
}

elasticity.outputs <- data.frame(names(hrlm$coefficients[2:length(hrlm$coefficients)]))
elasticity.outputs <- cbind(elasticity.outputs,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs) <- c("Variable","Elasticity")

elasticity.outputs$direction <- ifelse(elasticity.outputs$Elasticity > 0, "Positive", "Negative")



print(ggplot(data=elasticity.outputs, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Camera_Accessory - Linear Model") +xlab("Variables"))


multi <-data_final
multi <- multi[,-c(20:28)]
multi$number[which(multi$number==0)] <- 0.01
multi$Content.Marketing[which(multi$Content.Marketing==0)] <- 0.01
multi$per_order[which(multi$per_order==0)] <- 0.01
multi$TV[which(multi$TV==0)] <- 0.01

multi <- log(multi)
## First model ##
multi_model <- lm(gmv~.,multi)



all_vifs <- vif(multi_model)

 signif_all <- names(all_vifs)

 while(any(all_vifs > 1.1)){
  var_with_max_vif <- names(which(all_vifs == max(all_vifs)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=multi)  # re-build model with new formula
  all_vifs <- vif(selectedMod)
}

Multi_Final_model <- selectedMod




# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val1 <- train(myForm, data = multi, method = "lm",
               trControl = train.control)
# Summarize t1he results


# Elasticity Analysis
train1 <- multi
hrlm1<-Multi_Final_model
# estimating the elasticity coefficients
elasticity1 <- function(var){
  
  elax2 <-as.numeric(hrlm1$coefficients[var]*mean(train1[,var])/mean(train1$gmv))
  
  return(elax2)
} 
var_list <- list()

for(i in 2:length(hrlm1$coefficients)){
  
  var_list[i-1] <-elasticity1(names(hrlm1$coefficients)[i])
  
}

elasticity.outputs1 <- data.frame(names(hrlm1$coefficients[2:length(hrlm1$coefficients)]))
elasticity.outputs1 <- cbind(elasticity.outputs1,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs1) <- c("Variable","Elasticity")

elasticity.outputs1$direction <- ifelse(elasticity.outputs1$Elasticity > 0, "Positive", "Negative")



ggplot(data=elasticity.outputs1, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Camera_Accessory- Multiplicative Model") +xlab("Variables")



Home_koyck<-data_final
#gmv Lag 1
Home_Koyck<-slide(Home_koyck,Var="gmv",slideBy =-1)
Home_Koyck<-na.omit(Home_koyck)
Home_Koyck<-scale(Home_koyck)
Home_Koyck<-data.frame(Home_koyck)

# Build Kyock model
Koy_model <- lm(gmv~.,Home_koyck)
all_vifs <- vif(Koy_model)
 signif_all <- names(all_vifs)

 while(any(all_vifs > 2)){
  var_with_max_vif <- names(which(all_vifs == max(all_vifs)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=Home_koyck)  # re-build model with new formula
  all_vifs <- vif(selectedMod)
}

kyock_Final_model <- selectedMod



# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val2 <- train(myForm, data = Home_koyck, method = "lm",
               trControl = train.control)
# Summarize t1he results


# Elasticity Analysis
train2 <- Home_koyck
hrlm2<-kyock_Final_model
# estimating the elasticity coefficients
elasticity2 <- function(var){
  
  elax2 <-as.numeric(hrlm2$coefficients[var]*mean(train2[,var])/mean(train2$gmv))

  return(elax2)
} 
var_list <- list()

for(i in 2:length(hrlm2$coefficients)){
  
  var_list[i-1] <-elasticity2(names(hrlm2$coefficients)[i])
  
}

elasticity.outputs <- data.frame(names(hrlm2$coefficients[2:length(hrlm2$coefficients)]))
elasticity.outputs <- cbind(elasticity.outputs,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs) <- c("Variable","Elasticity")

elasticity.outputs$direction <- ifelse(elasticity.outputs$Elasticity > 0, "Positive", "Negative")



ggplot(data=elasticity.outputs, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Camera_Accessory - Koyck Model") +xlab("Variables")

Dis_Model <- data_final
Dis_model <- slide(Dis_Model, Var = "gmv",slideBy = -1)
Dis_model <- slide(Dis_model, Var = "gmv",slideBy = -2)
Dis_model <- slide(Dis_model, Var = "gmv",slideBy = -3)
Dis_model <- na.omit(Dis_model)
Dis_model <- scale(Dis_model)
Dis_model <- data.frame(Dis_model)

dist_model <- lm(gmv~.,Dis_model)



all_vif <- vif(dist_model)
signif_all <- names(all_vif)

 while(any(all_vif > 2)){
  var_with_max_vif <- names(which(all_vif == max(all_vif)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=Dis_model)  # re-build model with new formula
  all_vif <- vif(selectedMod)
}

Distributed_Final_model <- selectedMod




# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val <- train(myForm, data =Dis_model , method = "lm",
               trControl = train.control)
# Summarize t1he results


# Elasticity Analysis
train <- Dis_model
hrlm<-Distributed_Final_model
# estimating the elasticity coefficients
elasticity <- function(var){
  elax1 <-as.numeric(hrlm$coefficients[var]*mean(train[,var])/mean(train$gmv))
  return(elax1)
} 
var_list <- list()

for(i in 2:length(hrlm$coefficients)){
  
  var_list[i-1] <- elasticity(names(hrlm$coefficients)[i])
  
}

elasticity.outputs <- data.frame(names(hrlm$coefficients[2:length(hrlm$coefficients)]))
elasticity.outputs <- cbind(elasticity.outputs,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs) <- c("Variable","Elasticity")

elasticity.outputs$direction <- ifelse(elasticity.outputs$Elasticity > 0, "Positive", "Negative")



ggplot(data=elasticity.outputs, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Camera_Accessory- Distributed_lag Model") +xlab("Variables")


Multi_dist <-data_final[,-c(20:28)]
Multi_Dis_model_1 <- slide(Multi_dist, Var = "gmv",slideBy = -1)
Multi_Dis_model_1 <- slide(Multi_Dis_model_1, Var = "gmv",slideBy = -2)
Multi_Dis_model_1 <- slide(Multi_Dis_model_1, Var = "gmv",slideBy = -3)
Multi_dist <- na.omit(Multi_Dis_model_1)

Multi_dist$Content.Marketing[which(Multi_dist$Content.Marketing==0)] <-1
Multi_dist$per_order[which(Multi_dist$per_order==0)] <-0.01
Multi_dist$number[which(Multi_dist$number==0)] <-0.01
Multi_dist$TV[which(Multi_dist$TV==0)] <-0.01
Multi_dist <- log(Multi_dist)

distMulti <- lm(gmv~., Multi_dist)



all_vif <- vif(distMulti )
signif_all <- names(all_vif)

 while(any(all_vif > 1.2)){
  var_with_max_vif <- names(which(all_vif == max(all_vif)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=Multi_dist)  # re-build model with new formula
  all_vif <- vif(selectedMod)
}

DistributedMulti_Final_model <- selectedMod



# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val <- train(myForm, data =Multi_dist , method = "lm",
               trControl = train.control)
# Summarize t1he results


# estimating the elasticity coefficients
train <- Multi_dist

grlm <-DistributedMulti_Final_model 
elasticity <- function(var){
  
  elax1 <-as.numeric(grlm$coefficients[var]*mean(train[,var])/mean(train$gmv))
  
  return(elax1)
} 

var_list <- list()

for(i in 2:length(grlm$coefficients)){
  
  var_list[i-1] <-elasticity(names(grlm$coefficients)[i])
  
}

elasticity.outputs <- data.frame(names(grlm$coefficients[2:length(grlm$coefficients)]))
elasticity.outputs <- cbind(elasticity.outputs,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs) <- c("Variable","Elasticity")

elasticity.outputs$direction <- ifelse(elasticity.outputs$Elasticity > 0, "Positive", "Negative")



ggplot(data=elasticity.outputs, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Camera_Accessory - Multi. & DL model") +xlab("Variables")



```

# Model on Game Accessories Final {data-navmenu="Project Sections"}
```{r echo=FALSE}

options(warn=-1)
library(magrittr)
library(knitr)
library(DT)
library(ggplot2);
library(plyr);
library(dplyr);
library(Hmisc);
library(broom);
library(xts);
library(lubridate)
library(cluster)
library(zoo)
library(car)
library(MASS)
library(caret)
library(DataCombine)
options(warn=-1)
# Function for Various Model
data2_final <- read.csv("gaming_accesory_final")
# Building the Baisc Linear regression Model
Linear_model <-data2_final
Linear_model <- scale(Linear_model)
Linear_model <-data.frame(Linear_model)
model_1 <- lm(gmv~.,Linear_model)



all_vifs <- vif(model_1)

 signif_all <- names(all_vifs)

 while(any(all_vifs > 2)){
  var_with_max_vif <- names(which(all_vifs == max(all_vifs)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=Linear_model)  # re-build model with new formula
  all_vifs <- vif(selectedMod)
}

##Final Model 
Linear_Final_model <- selectedMod





# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val <- train(myForm, data = Linear_model, method = "lm",
               trControl = train.control)
# Summarize the results



# Elasticity Analysis
train <- Linear_model
hrlm<-Linear_Final_model
# estimating the elasticity coefficients
elasticity <- function(var){
  
  elax1 <-as.numeric(hrlm$coefficients[var]*mean(train[,var])/mean(train$gmv))
  
  return(elax1)
} 
var_list <- list()

for(i in 2:length(hrlm$coefficients)){
  
  var_list[i-1] <-elasticity(names(hrlm$coefficients)[i])
  
}

elasticity.outputs <- data.frame(names(hrlm$coefficients[2:length(hrlm$coefficients)]))
elasticity.outputs <- cbind(elasticity.outputs,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs) <- c("Variable","Elasticity")

elasticity.outputs$direction <- ifelse(elasticity.outputs$Elasticity > 0, "Positive", "Negative")



print(ggplot(data=elasticity.outputs, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Game_Accessory - Linear Model") +xlab("Variables"))


multi <-data_final
multi <- multi[,-c(20:28)]
multi$number[which(multi$number==0)] <- 0.01
multi$Content.Marketing[which(multi$Content.Marketing==0)] <- 0.01
multi$per_order[which(multi$per_order==0)] <- 0.01
multi$TV[which(multi$TV==0)] <- 0.01

multi <- log(multi)
## First model ##
multi_model <- lm(gmv~.,multi)



all_vifs <- vif(multi_model)

 signif_all <- names(all_vifs)

 while(any(all_vifs > 1.1)){
  var_with_max_vif <- names(which(all_vifs == max(all_vifs)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=multi)  # re-build model with new formula
  all_vifs <- vif(selectedMod)
}

Multi_Final_model <- selectedMod




# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val1 <- train(myForm, data = multi, method = "lm",
               trControl = train.control)
# Summarize t1he results


# Elasticity Analysis
train1 <- multi
hrlm1<-Multi_Final_model
# estimating the elasticity coefficients
elasticity1 <- function(var){
  
  elax2 <-as.numeric(hrlm1$coefficients[var]*mean(train1[,var])/mean(train1$gmv))
  
  return(elax2)
} 
var_list <- list()

for(i in 2:length(hrlm1$coefficients)){
  
  var_list[i-1] <-elasticity1(names(hrlm1$coefficients)[i])
  
}

elasticity.outputs1 <- data.frame(names(hrlm1$coefficients[2:length(hrlm1$coefficients)]))
elasticity.outputs1 <- cbind(elasticity.outputs1,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs1) <- c("Variable","Elasticity")

elasticity.outputs1$direction <- ifelse(elasticity.outputs1$Elasticity > 0, "Positive", "Negative")



ggplot(data=elasticity.outputs1, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Game_Accessory- Multiplicative Model") +xlab("Variables")



Home_koyck<-data_final
#gmv Lag 1
Home_Koyck<-slide(Home_koyck,Var="gmv",slideBy =-1)
Home_Koyck<-na.omit(Home_koyck)
Home_Koyck<-scale(Home_koyck)
Home_Koyck<-data.frame(Home_koyck)

# Build Kyock model
Koy_model <- lm(gmv~.,Home_koyck)
all_vifs <- vif(Koy_model)
 signif_all <- names(all_vifs)

 while(any(all_vifs > 2)){
  var_with_max_vif <- names(which(all_vifs == max(all_vifs)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=Home_koyck)  # re-build model with new formula
  all_vifs <- vif(selectedMod)
}

kyock_Final_model <- selectedMod



# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val2 <- train(myForm, data = Home_koyck, method = "lm",
               trControl = train.control)
# Summarize t1he results


# Elasticity Analysis
train2 <- Home_koyck
hrlm2<-kyock_Final_model
# estimating the elasticity coefficients
elasticity2 <- function(var){
  
  elax2 <-as.numeric(hrlm2$coefficients[var]*mean(train2[,var])/mean(train2$gmv))

  return(elax2)
} 
var_list <- list()

for(i in 2:length(hrlm2$coefficients)){
  
  var_list[i-1] <-elasticity2(names(hrlm2$coefficients)[i])
  
}

elasticity.outputs <- data.frame(names(hrlm2$coefficients[2:length(hrlm2$coefficients)]))
elasticity.outputs <- cbind(elasticity.outputs,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs) <- c("Variable","Elasticity")

elasticity.outputs$direction <- ifelse(elasticity.outputs$Elasticity > 0, "Positive", "Negative")



ggplot(data=elasticity.outputs, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Game_Accessory - Koyck Model") +xlab("Variables")

Dis_Model <- data_final
Dis_model <- slide(Dis_Model, Var = "gmv",slideBy = -1)
Dis_model <- slide(Dis_model, Var = "gmv",slideBy = -2)
Dis_model <- slide(Dis_model, Var = "gmv",slideBy = -3)
Dis_model <- na.omit(Dis_model)
Dis_model <- scale(Dis_model)
Dis_model <- data.frame(Dis_model)

dist_model <- lm(gmv~.,Dis_model)



all_vif <- vif(dist_model)
signif_all <- names(all_vif)

 while(any(all_vif > 2)){
  var_with_max_vif <- names(which(all_vif == max(all_vif)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=Dis_model)  # re-build model with new formula
  all_vif <- vif(selectedMod)
}

Distributed_Final_model <- selectedMod




# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val <- train(myForm, data =Dis_model , method = "lm",
               trControl = train.control)
# Summarize t1he results


# Elasticity Analysis
train <- Dis_model
hrlm<-Distributed_Final_model
# estimating the elasticity coefficients
elasticity <- function(var){
  elax1 <-as.numeric(hrlm$coefficients[var]*mean(train[,var])/mean(train$gmv))
  return(elax1)
} 
var_list <- list()

for(i in 2:length(hrlm$coefficients)){
  
  var_list[i-1] <- elasticity(names(hrlm$coefficients)[i])
  
}

elasticity.outputs <- data.frame(names(hrlm$coefficients[2:length(hrlm$coefficients)]))
elasticity.outputs <- cbind(elasticity.outputs,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs) <- c("Variable","Elasticity")

elasticity.outputs$direction <- ifelse(elasticity.outputs$Elasticity > 0, "Positive", "Negative")



ggplot(data=elasticity.outputs, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Game_Accessory- Distributed_lag Model") +xlab("Variables")


Multi_dist <-data_final[,-c(20:28)]
Multi_Dis_model_1 <- slide(Multi_dist, Var = "gmv",slideBy = -1)
Multi_Dis_model_1 <- slide(Multi_Dis_model_1, Var = "gmv",slideBy = -2)
Multi_Dis_model_1 <- slide(Multi_Dis_model_1, Var = "gmv",slideBy = -3)
Multi_dist <- na.omit(Multi_Dis_model_1)

Multi_dist$Content.Marketing[which(Multi_dist$Content.Marketing==0)] <-1
Multi_dist$per_order[which(Multi_dist$per_order==0)] <-0.01
Multi_dist$number[which(Multi_dist$number==0)] <-0.01
Multi_dist$TV[which(Multi_dist$TV==0)] <-0.01
Multi_dist <- log(Multi_dist)

distMulti <- lm(gmv~., Multi_dist)



all_vif <- vif(distMulti )
signif_all <- names(all_vif)

 while(any(all_vif > 1.2)){
  var_with_max_vif <- names(which(all_vif == max(all_vif)))    # get the var with max vif
  signif_all <- signif_all[!(signif_all) %in% var_with_max_vif]  # remove
  myForm <- as.formula(paste("gmv ~ ", paste (signif_all, collapse=" + "), sep=""))  # new formula
  selectedMod <- lm(myForm, data=Multi_dist)  # re-build model with new formula
  all_vif <- vif(selectedMod)
}

DistributedMulti_Final_model <- selectedMod



# Define training control
set.seed(123)
train.control <- trainControl(method = "cv", number = 10)
# Train the model
cross_val <- train(myForm, data =Multi_dist , method = "lm",
               trControl = train.control)
# Summarize t1he results


# estimating the elasticity coefficients
train <- Multi_dist

grlm <-DistributedMulti_Final_model 
elasticity <- function(var){
  
  elax1 <-as.numeric(grlm$coefficients[var]*mean(train[,var])/mean(train$gmv))
  
  return(elax1)
} 

var_list <- list()

for(i in 2:length(grlm$coefficients)){
  
  var_list[i-1] <-elasticity(names(grlm$coefficients)[i])
  
}

elasticity.outputs <- data.frame(names(grlm$coefficients[2:length(grlm$coefficients)]))
elasticity.outputs <- cbind(elasticity.outputs,do.call(rbind.data.frame, var_list))
colnames(elasticity.outputs) <- c("Variable","Elasticity")

elasticity.outputs$direction <- ifelse(elasticity.outputs$Elasticity > 0, "Positive", "Negative")



ggplot(data=elasticity.outputs, aes(x=reorder(Variable,Elasticity),y=Elasticity)) +
  geom_bar(position="dodge",stat="identity") + 
  coord_flip() +
  ggtitle("Game_Accessory - Multi. & DL model") +xlab("Variables")



```


# Conculsion Made {data-navmenu="Project Sections"}

############################################### Home Audio Final #####################################################################
* Linear Model
    + Adjusted R-squared:  0.391   
    + RMSE (10 - CV):      0.979
  
* Multiplicative Model
    + Adjusted R-squared:  0.318 
    + RMSE (10 - CV):       0.057

* Kyock Model
    + Adjusted R-squared:  0.391 
    + RMSE (10 - CV):      121.07

* Distributed Lag model
    + Adjusted R-squared:  0.361 
    + RMSE (10 - CV):      1.038  

* Multiplicative +Distributed Lag model
    + Adjusted R-squared:  0.3685 
    + RMSE (10 - CV):      0.053


############################################### Camera Accessory Final #####################################################################
* Linear Model
    + Adjusted R-squared:  0.419  
    + RMSE (10 - CV):      0.92
  
* Multiplicative Model
    + Adjusted R-squared:  0.628
    + RMSE (10 - CV):      0.227 

* Kyock Model
    + Adjusted R-squared:  0.391 
    + RMSE (10 - CV):      246.6

* Distributed Lag model
    + Adjusted R-squared:  0.361 
    + RMSE (10 - CV):      1.250

* Multiplicative +Distributed Lag model
    + Adjusted R-squared:  0.3685 
    + RMSE (10 - CV):      2.23
    
############################################### Gaming Accessory Final #####################################################################
* Linear Model
    + Adjusted R-squared:    0.637
    + RMSE (10 - CV):        0.769
  
* Multiplicative Model
    + Adjusted R-squared:   0.56 
    + RMSE (10 - CV):       0.18

* Kyock Model
    + Adjusted R-squared:   0.56
    + RMSE (10 - CV):       0.189

* Distributed Lag model
    + Adjusted R-squared:   0.63 
    + RMSE (10 - CV):       105.26

* Multiplicative +Distributed Lag model
    + Adjusted R-squared:   0.6705
    + RMSE (10 - CV):       0.731  
